Scaling laws of trophic level and generality vary across latitude

### 2014-06-23 manuscript/latitudepaper.tex
Try non-linear regressions next week.
Corrected table 2, inserted figures.

@@

The scaling rules of mean trophic level and generality, however, did vary over latitude. 
Mean trophic level increased with latitude ($\beta$=0.011, $p$<0.001) and with species richness 
($\beta$=0.633, $p$<0.001), but both trends were weakened by an interaction between latitude and species-richness 
($\beta$=-0.008, $p$=0.001). The best-fitting model for mean trophic 
level did not include a connectance term. The increase in mean trophic level with species richness was highest for 
estuarine food webs ($\beta$=0.633, $p$<0.001) and lower for freshwater ($\beta$=0.259, $p$=0.002), terrestrial 
($\beta$=0.234, $p$=0.005), and marine food webs ($\beta$=0.152, $p$<0.001). For food webs with high species richness, 
trophic level declined with latitude while trophic level in species-poor webs showed the opposite trend 
(Fig. \ref{TLfig}). The number of species for which the slope of trophic level over latitude changed from negative to 
positive varied across ecosystem types.

Generality showed the opposite trend, increasing with latitude for webs with high species richness and decreasing with
latitude for species-poor webs (Fig. \ref{genfig}).
This increase was driven by a positive interaction between latitude and species richness ($\beta$=0.014, $p$=0.002), as 
the main effect of latitude was negative ($\beta$=-0.018, $p$=0.002). Generality also decreased with species richness 
for estuarine food webs ($\beta$=-0.150, $p$=0.002) but increased with species richness for freshwater, terrestrial, 
and marine webs ($\beta$=0.453, $p$=0.005; $\beta$=0.523, $p$=0.006; and $\beta$=0.675, $p$=0.001; respectively). 
Generality increased with connectance equally in all ecotypes and across all latitudes ($\beta$=0.799, $p$<0.001).

@@

\begin{center}
\begin{table}[!h]
\caption{Symbols for and descriptions of food-web properties.}
\label{symboltable}
\begin{tabular}{c l l}
\hline
Symbol      & Name & Description \\
\hline
S & Species richness & Number of trophic species \\
LS & Links per species & Mean number of links per taxon \\
C & Connectance & Number of observed links divided by the number of possible links ($L/S^{2}$) \\
\%Top & \% Top predators & Percentage of taxa without consumers \\
\%Int & \% Intermediate consumers & Percentage of taxa with both consumers and resources \\
\%Basal & \% Basal Resources & Percentage of taxa without resources \\
\%Herb	& \% Herbivores	& Percentage of herbivores and detrivores (taxa that feed on basal taxa) \\
\%Omni & \%Omnivores & Percentage of omnivores (taxa that feed on ≥2 taxa with different trophic levels) \\
Gen & Generality & Mean number of resources per taxon \\
GenSD & SD of generality & Standard deviation of resources per taxon \\
Vul & Vulnerability & Mean number of consumers per taxon \\
VulSD & SD of vulnerability & Standard deviation of consumers per taxon \\
LinkSD & SD of links per species & Standard deviation of links (consumers and resources) per taxon \\
SWTL & Mean short-weighted trophic level & Short-weighted trophic level averaged across taxa \\
Path & Path length & Characteristic path length, the mean shortest food chain between species pairs \\
\hline
\end{tabular}
\end{table}
% NODF & Average Nestedness & Degree to which interactions among specialists are subsets or interactions among generalists \\
% Chain & Chain length & Mean food chain length \\
% Cluster & Clustering coefficient & Mean clustering coefficient (probability that two taxa linked to the same taxon are also linked) \\

\begin{center}
\begin{table}[!h]
\caption{Full models for S, LS, and C.}
\label{symbols}
\begin{tabular}{c c c c c c c}
\hline
 & \multicolumn{2}{S} & \multicolumn{2}{C} & \multicolumn{2}{LS} \\
\hline
Effect & Estimate & $p$-value & Estimate & $p$-value & Estimate & $p$-value \\
\hline
Latitude 			& 0.002  & 0.870  & -0.006 & 0.460  & -0.004 & 0.6115 \\ 
Estuary 			& 1.078  & 0.018  & -0.809 & 0.008  & 0.269 & 0.363 \\
Lake 				& 1.351  & 0.002  & -1.069 & <0.001 & 0.282 & 0.315 \\
Marine 				& 1.127  & <0.001 & -0.761 & <0.001 & 0.366 & 0.012 \\
Stream 				& 1.319  & <0.001 & -1.260 & <0.001 & 
Terrestrial 		& 1.097  & <0.001 & -0.919 & <0.001 & 
Latitude:Lake 		& -0.004 & 0.796  & 0.011  & 0.314  & 
Latitude:Marine 	& 0.003  & 0.842  & 0.001  & 0.896  & 
Latitude:Stream 	& 0.004  & 0.780  & 0.009  & 0.310  & 
Latitude:Terrestrial & 0.001 & 0.920  & 0.003  & 0.712  &

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    Look into non-linear regressions for all properties (nls?)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The scaling rules of mean trophic level and generality, however, did vary over latitude. 
Mean trophic level increased with latitude ($\beta$=0.011, $p$<0.001) and with species richness 
($\beta$=0.633, $p$<0.001), but both trends were weakened by an interaction between latitude and species-richness 
($\beta$=-0.008, $p$=0.001). The best-fitting model for mean trophic 
level did not include a connectance term. The increase in mean trophic level with species richness was highest for 
estuarine food webs ($\beta$=0.633, $p$<0.001) and lower for freshwater ($\beta$=0.259, $p$=0.002), terrestrial 
($\beta$=0.234, $p$=0.005), and marine food webs ($\beta$=0.152, $p$<0.001). For food webs with high species richness, 
trophic level declined with latitude while trophic level in species-poor webs showed the opposite trend 
(Fig. \ref{TL_all}). The number of species for which the slope of trophic level over latitude changed from negative to 
positive varied across ecosystem types.

Generality showed the opposite trend, increasing with latitude for webs with high species richness and decreasing with
latitude for species-poor webs (Fig. \ref{gen_all}).
This increase was driven by a positive interaction between latitude and species richness ($\beta$=0.014, $p$=0.002), as 
the main effect of latitude was negative ($\beta$=-0.018, $p$=0.002). Generality also decreased with species richness 
for estuarine food webs ($\beta$=-0.150, $p$=0.002) but increased with species richness for freshwater, terrestrial, 
and marine webs ($\beta$=0.453, $p$=0.005; $\beta$=0.523, $p$=0.006; and $\beta$=0.675, $p$=0.001; respectively). 
Generality increased with connectance equally in all ecotypes and across all latitudes ($\beta$=0.799, $p$<0.001).

@@

\begin{center}
\begin{table}[!h]
\caption{Symbols for and descriptions of food-web properties.}
\label{symboltable}
\begin{tabular}{c l l}
\hline
Symbol      & Name & Description \\
\hline
S & Species richness & Number of trophic species \\
LS & Links per species & Mean number of links per taxon \\
C & Connectance & Number of observed links divided by the number of possible links ($L/S^{2}$) \\
\%Top & \% Top predators & Percentage of taxa without consumers \\
\%Int & \% Intermediate consumers & Percentage of taxa with both consumers and resources \\
\%Basal & \% Basal Resources & Percentage of taxa without resources \\
\%Herb	& \% Herbivores	& Percentage of herbivores and detrivores (taxa that feed on basal taxa) \\
\%Omni & \%Omnivores & Percentage of omnivores (taxa that feed on ≥2 taxa with different trophic levels) \\
Gen & Generality & Mean number of resources per taxon \\
GenSD & SD of generality & Standard deviation of resources per taxon \\
Vul & Vulnerability & Mean number of consumers per taxon \\
VulSD & SD of vulnerability & Standard deviation of consumers per taxon \\
LinkSD & SD of links per species & Standard deviation of links (consumers and resources) per taxon \\
SWTL & Mean short-weighted trophic level & Short-weighted trophic level averaged across taxa \\
Path & Path length & Characteristic path length, the mean shortest food chain between species pairs \\
\hline
\end{tabular}
\end{table}
\end{center}
% NODF & Average Nestedness & Degree to which interactions among specialists are subsets or interactions among generalists \\
% Chain & Chain length & Mean food chain length \\
% Cluster & Clustering coefficient & Mean clustering coefficient (probability that two taxa linked to the same taxon are also linked) \\

\begin{center}
\begin{table}[!h]
\caption{Full models for S, LS, and C.}
\label{symbols}
\begin{tabular}{c c c c c c c}
\hline
 & \multicolumn{2}{c}{S} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{LS} \\
\hline
Effect & Estimate & $p$-value & Estimate & $p$-value & Estimate & $p$-value \\
\hline
Latitude 			& 0.002  & 0.873  & -0.006 & 0.480  & -0.004 & 0.613 \\ 
Estuary 			& 1.078  & 0.022  & -0.809 & 0.012  & 0.269 & 0.362 \\
Freshwater 			& 1.347  & \textless0.001  & -1.229 & \textless0.001 & 0.118 & 0.394 \\
Marine 				& 1.127  & \textless0.001 & -0.761 & \textless0.001 & 0.366 & 0.012 \\
Terrestrial 		& 1.097  & \textless0.001 & -0.919 & \textless0.001 & 0.178 & 0.354\\
Latitude:Freshwater & 0.002  & 0.902  & 0.010  & 0.299  & 0.012 & 0.194\\
Latitude:Marine 	& 0.003  & 0.847  & 0.001  & 0.902  & 0.004 & 0.662 \\
Latitude:Terrestrial & 0.001 & 0.923  & 0.003  & 0.724  & 0.005 & 0.597 \\
\end{tabular}
\end{table}
\end{center}

@@

\section*{Figures}

\begin{figure}[!h]
\label{gen_all}
\includegraphics[width=.9\textwidth]{Figures/gen_all.eps}
\caption{Relationships between mean generality and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
\end{figure}

\begin{figure}[!h]
\label{TL_all}
\includegraphics[width=.9\textwidth]{Figures/TL_all.eps}
\caption{Relationships between mean trophic level and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
\end{figure}
